%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Michael Ha} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +1 (438) 495-8068 ~ \href{mailto:michael.ha@mail.mcgill.ca}{\raisebox{-0.2\height}\faEnvelope\  \underline{michael.ha@mail.mcgill.ca}} ~ 
    \href{https://www.linkedin.com/in/michael-ha-a19575296/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/michael-ha}}  ~
    \href{https://github.com/tsunam-1}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/tsunam-1}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McGill University}{Aug. 2024 -- Dec. 2028}
      {Bachelor of Engineering in Software Engineering Co-Op}{Montreal, Quebec}
        \resumeItemListStart
            \resumeItem{GPA: 3.87}
        \resumeItemListEnd
    \resumeSubheading
      {John Abbott College}{Aug. 2022 -- May 2024}
      {Diploma of College Studies in Sciences}
      {Sainte-Anne-de-Bellevue, Quebec}
        \resumeItemListStart
            \resumeItem{R score: 34.519}
            \resumeItem{Four-time Dean's list recipient and English Honours Portfolio (excellence in written English)}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: English (native), French (native), Vietnamese (elementary)} \\
     \textbf{Programming Languages}{: Java, Python, C, C\#, Bash, JavaScript, HTML/CSS, VHDL, R, Umple} \\
     \textbf{Developer Tools}{: IntelliJ, PyCharm, VS Code, Eclipse} \\
     \textbf{Technologies/Frameworks}{: Node.js, Express.js, EJS, Flask, Bootstrap, JavaFX, Tkinter, Selenium, BeautifulSoup, Linux, GitHub, SCRUM} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Portfolio Website} $|$ \emph{HTML, CSS, JavaScript, Node.js, Express.js, EJS}}{Jan. 2026}
          \resumeItemListStart
            \resumeItem{Developed a personal portfolio website to showcase my projects and skills using EJS templating with Node.js and Express.js for server-side rendering (backend).}
            \resumeItem{Implemented a responsive frontend using HTML, CSS, and JavaScript to enhance user experience and accessibility.}
            \resumeItem{Developed a resume parsing feature to extract project information from uploaded resume and dynamically generate the project section page.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Automated Courier Robot with BrickPi} $|$ \emph{Python}}{Sep. 2025 -- Dec. 2025}
          \resumeItemListStart
            \resumeItem{Collaborated in a team of 6 to iteratively design and implement hardware and software for a small-scale autonomous delivery robot using EV3 sensors, motors, and Raspberry Pi, with full version control integration.}
            \resumeItem{Architected multi-threaded system handling synchronized robot navigation, real-time sensor alignment, color-based object detection, and state machine-driven event handling for autonomous task execution.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Cheese Manager MVC} $|$ \emph{Java, JavaFX, Umple}}{Sep. 2025 -- Dec. 2025}
          \resumeItemListStart
            \resumeItem{Engineered a comprehensive MVC application in a 7-person team, designing a domain model with integrated state machine logic, backend controller layer, and JavaFX GUI for managing cheese inventory, orders, and sales in wholesale supply chain scenarios.}
            \resumeItem{Achieved 100% test acceptance by implementing 200+ distinct test scenarios using Gherkin specifications and Cucumber framework, ensuring robust validation of all controller operations and business logic.
            }
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Anilist Automated Liker} $|$ \emph{Python, Selenium, Tkinter}}{June 2025}
          \resumeItemListStart
            \resumeItem{Developed an automation tool leveraging Selenium for web scraping and Python scripting to streamline repetitive user interaction tasks on the Anilist platform with timeout validations.}
            \resumeItem{Engineered an intuitive Tkinter-based GUI enabling users to securely manage local authentication credentials and customize automation parameters, while implementing intelligent rate-limiter to respect API constraints.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Population Common Ancestor Simulation} $|$ \emph{R}}{Apr. 2024 -- May 2024}
          \resumeItemListStart
            \resumeItem{Collaborated in a two-person team to build a probabilistic simulation modeling ancestry relationships and computing the most recent common ancestor across varying population demographics.}
            \resumeItem{Applied advanced statistical visualization techniques in R to analyze population trends and distribution patterns, translating complex genetic data into actionable insights.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------INVOLVEMENT---------------
\section{Other Experience}
    \resumeSubHeadingListStart
        \resumeSubheading{@Hack 2025 (CTF Hackathon)}{Mar. 2025}{Participant}{Montreal, Quebec}
            \resumeItemListStart
                \resumeItem{Collaborated in a team of 2 to tackle CTF-style security challenges.}
                \resumeItem{Won first prize in the hardware time-based challenge.}
            \resumeItemListEnd
        \resumeSubheading{French Tutoring}{Jan. 2024 -- May 2024}{Tutor}{John Abbott College}
            \resumeItemListStart
                \resumeItem{Provided weekly academic support to beginner and intermediate French learners through the CAF - Moniteurs de Français program.}
                \resumeItem{Helped students strengthen French grammar, reading comprehension, vocabulary, pronunciation, and conversational skills in a structured, cooperative, and peer-led setting.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}
